19th International Satisfiability Modulo Theories Competition (SMT-COMP 2024): Rules and Procedures

### 2024-05-07 rules/rules24.tex
Added the new smtcomp tool to the rules document.

  \item {\bf Memory limits.}  \emergencystretch.5cm
  The memory limits for the single query, incremental, unsat-core, and model-validation tracks are reduced to 30\,GB.
%
  \rationale{The reason are hardware limits of the new execution platform.}

  \item {\bf Proof track.}  \emergencystretch.5cm
  The previously experimental evaluation proof track will be discontinued.
%
  \rationale{There are three reasons that led to this decision. 
             First, we were unable to find a way of turning the proof track into a competition that would not lead to 
             an unmanageable amount of overhead on the competition organizers or the participants.
             Second, we have collected vast amounts of data in the last two years and thoroughly evaluating it takes time.
             Third, this year we would need to restrict the allowed proof size due to hardware limits of the new execution platform.}
\end{itemize}

@@

\header{Tools.} \label{tools}
The competition uses a number of tools/scripts to run the competition. In the
following, we briefly describe these tools. Unless stated otherwise, these
tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
\begin{itemize}
  \item \textbf{Benchmark Selection.} We use a script to implement the
    benchmark selection policy described on page~\pageref{benchmark-selection}.
    It takes a seed for the random benchmark selection. The same seed is used
    for all tools requiring randomisation.
  \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
    competition to ensure that tools do not rely on syntactic features to
    identify benchmarks. The scrambler can be found at
    \url{https://github.com/SMT-COMP/scrambler}.
  \item \textbf{Trace Executor.} This tool is used in the \inctrack to emulate
    an on-line interaction between an SMT solver and a client application and
    is available at \url{https://github.com/SMT-COMP/trace-executor}
  \item \textbf{Post-Processors.} These are used by the \executionservice to translate the
    output of tools to the format required for scoring. All post-processors (per
    track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
  \item \textbf{Scoring.} We use a script to implement the scoring computation
    described on in Section~\ref{sec:scoring}. It also includes the scoring
    computations used in previous competitions (since 2015).
\end{itemize}

>>>>

  \item {\bf Memory limits.}  \emergencystretch.5cm
  The memory limits for the single query, incremental, unsat-core, and model-validation tracks are reduced to 30\,GB.
%
  \rationale{The reasons are hardware limits of the new execution platform.}

  \item {\bf Proof track.}  \emergencystretch.5cm
  The previously experimental evaluation proof track will be discontinued.
%
  \rationale{There are three reasons that led to this decision. 
             First, we were unable to find a way of turning the proof track into a competition that would not lead to 
             an unmanageable amount of overhead on the competition organizers or the participants.
             Second, we have collected vast amounts of data in the last two years and thoroughly evaluating it takes time.
             Third, this year we would need to restrict the allowed proof size due to hardware limits of the new execution platform.}

  \item {\bf Tools.}  \emergencystretch.5cm
    All the relevant scripts in \url{https://github.com/SMT-COMP/smt-comp} have been combined into one tool called \textbf{smtcomp}
    that is available at 
    \url{https://github.com/SMT-COMP/smt-comp.github.io}.
%
  \rationale{The reason for this new tool is that the sheer number of old scripts and their various locations 
             caused a lot of confusion to many new and several longtime participants.
             The tool also has better run time compared to some of the old scripts because it uses parallelization where possible.
             Moreover, it provides a nicer UI compared to the old scripts.}
\end{itemize}

@@

\header{Tools.} \label{tools}
The competition uses a number of tools/scripts to run the competition. In the
following, we briefly describe these tools.
\begin{itemize}
  \item \textbf{smtcomp.} This tool combines the functionality of most of the 
    scripts used in previous years and more. It is available at 
    \url{https://github.com/SMT-COMP/smt-comp.github.io}. Some of its functionalities include:
    \begin{itemize}
      \item \textbf{Benchmark Selection.} The tool has a command that executes the
        benchmark selection policy described on page~\pageref{benchmark-selection}.
        It takes a seed for the random benchmark selection. The same seed is used
        for all tools requiring randomisation.
      \item \textbf{Scoring.} The tool has a command that executes the scoring computation
        described on in Section~\ref{sec:scoring}. It also includes the scoring
        computations used in previous competitions (since 2015).
    \end{itemize}
    For a full list of the capabilities of the smtcomp tool and an explanation of all important commands
    see \url{https://github.com/SMT-COMP/smt-comp.github.io/blob/master/README.md}
  \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
    competition to ensure that tools do not rely on syntactic features to
    identify benchmarks. The scrambler can be found at
    \url{https://github.com/SMT-COMP/scrambler}.
  \item \textbf{Trace Executor.} This tool is used in the \inctrack to emulate
    an on-line interaction between an SMT solver and a client application and
    is available at \url{https://github.com/SMT-COMP/trace-executor}
  \item \textbf{Post-Processors.} These are used by the \executionservice to translate the
    output of tools to the format required for scoring. All post-processors (per
    track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
\end{itemize}
